Surface-driven registration method for the structure-informed segmentation of diffusion MR images\tnoteref{t1}

### 2016-03-10 Publications/2015-NeuroImage/responseLetter3.tex

\begin{document}
\hypersetup{linkcolor=black!60, citecolor=black!60, urlcolor=black!60}

\section*{Response letter to the manuscript no. NIMG-15-2877R1}

\bigskip
\noindent We thank the editors and the reviewers for revising our manuscript no. NIMG-15-2877R1 submitted to NeuroImage.
We appreciate the comments made by both reviewers, and considered them fully to improve our paper.
Please, find in the following paragraphs our point-by-point answer to the concerns raised by the reviewers,
  along with the description of the corresponding changes in the manuscript.
Text modifications in the manuscript are highlighted with a new font color, and attached notes indicate 
  which reviewer and comment the corresponding change is addressing to.

\bigskip
\bigskip
\subsection*{Reviewer \#1:}
\begin{reviewintro}
In general, I think the authors have done a good job of restructuring the paper to qualify the goals and implementation of the method. I have a few points.
\end{reviewintro}
\begin{reviewpoint}
The authors suggest that diffusion tractography is typically performed by mapping segmentations to the data. This is becoming less true. The HCP for one performs whole brain connectivity analysis. Nevertheless, these frameworks still require registration to structural space for projection to surface mesh representations and/or coaligning data. This may be worth mentioning or clarifying.
\end{reviewpoint}
\reply{%
We have introduced this discussion in lines 351--355.
}
\begin{reviewpoint}
I still find figure 2 really difficult to read anything from. It's not easy to read the labels in the coloured text, nor see the different histograms in figure 2 A. This is partly because many of the colours are light very similar i.e. for WM and bst. It does occur to me that not all distributions change that greatly with registration. Maybe stripping back figure A to only include WM, GM and possibly VdGM might help?
\end{reviewpoint}
\reply{%
We have made the following editions in this figure to make it more clear:
\begin{itemize}
\item Changed color palette to the ``Set1'' palette of the ColorBrewer tool\footnote{\url{http://colorbrewer2.org/}}, which has
  darker colors.
\item The darker colors allowed for thiner lines to represent the contours of the joint density plot in panel A, improving
  readability.
\item Better positioned labels in the panel A of this figure, using the Fruchterman-Reingold force-directed algorithm.
\item Matched the fonts of axis labels with the font used in the NeuroImage journal.
\end{itemize}
}
\begin{reviewpoint}
I find the clarification of how tratography might be unwarped in the response very helpful, but some clarification of the manuscript might be helpful. What do the authors mean by ``the resampling of the DWIs introduced by the correction method can be avoided, either by performing the posterior processing on the native dMRI space''. How does the native dMRI space differ from the DWIs here, or what is meant by posterior processing.
\end{reviewpoint}
\reply{%
We have reformulated that particular sentence (lines 57--59) and added a corresponding discussion in lines 348--356.
These editions are highly related to Comments \ref{com:1}, \ref{com:5} and \ref{com:6}.
}
\begin{reviewpoint}
In the appendix I think the B-spline variable (Eqs A.7 A.8)  should be defined in the text again
\end{reviewpoint}
\reply{%
We have defined introduced the definition of $\mathbf{g}_k$ in lines 122--123, right before the
  reference to the mentioned equations.
}

### 2016-03-10 Publications/2015-NeuroImage/figure05.tex
updated paper

% -*- root: 00-main.tex -*-
% @Author: Oscar Esteban
% @Date:   2015-04-09 13:06:32
% @Last Modified by:   Oscar Esteban
% @Last Modified time: 2015-04-09 15:52:17

@@

\begin{document}
\begin{tikzpicture}
  \node[inner sep=10pt, draw=black!40](fig03b) at (0,8.8)
    {\hspace*{20pt}\includegraphics[width=21cm]{figure05A}};
  \node[inner sep=10pt, draw=black!40](fig03c) at (0,0)
    {\hspace*{20pt}\includegraphics[width=21cm]{figure05B}};
  \node[circle, text=black!75, inner sep=0] at (-10.65,12.0) {\Huge \textbf{A}};
  \node[circle, text=black!75, inner sep=0] at (-10.65,4.05) {\Huge \textbf{B}};
\end{tikzpicture}
\end{document}

>>>>

% -*- root: 00-main.tex -*-
% @Author: Oscar Esteban
% @Date:   2015-04-09 13:06:32
% @Last Modified by:   oesteban
% @Last Modified time: 2016-03-09 13:49:09

@@

\begin{document}
\begin{tikzpicture}
  \node[inner sep=10pt, draw=black!40](fig05b) at (0,8.8)
    {\hspace*{20pt}\includegraphics[width=21cm]{figure05A}};
  \node[inner sep=10pt, draw=black!40](fig05c) at (0,0)
    {\hspace*{20pt}\includegraphics[width=21cm]{figure05B}};
  \node[circle, text=black!75, inner sep=0] at (-10.65,12.0) {\Huge \textbf{A}};
  \node[circle, text=black!75, inner sep=0] at (-10.65,4.05) {\Huge \textbf{B}};
\end{tikzpicture}
\end{document}

### 2016-03-10 Publications/2015-NeuroImage/figure06.tex
updated paper

% -*- root: 00-main.tex -*-
% @Author: Oscar Esteban
% @Date:   2015-04-09 14:39:30
% @Last Modified by:   Oscar Esteban
% @Last Modified time: 2015-04-09 15:54:48

@@

\begin{document}
  \begin{tikzpicture}
    \node[inner sep=15pt, draw=black!40](fig05a) at (0,12.0)
      {\hspace*{20pt}\includegraphics[width=21cm]{figure06A}};
    \node[inner sep=15pt, draw=black!40](fig05b) at (0,0)
      {\hspace*{20pt}\includegraphics[width=21cm]{figure06B}};
    \node[circle, text=black!75, inner sep=0] at (-10.65,18.6) {\Huge \textbf{A}};
    \node[circle, text=black!75, inner sep=0] at (-10.65,3.5) {\Huge \textbf{B}};
  \end{tikzpicture}
\end{document}

>>>>

% -*- root: 00-main.tex -*-
% @Author: Oscar Esteban
% @Date:   2015-04-09 14:39:30
% @Last Modified by:   oesteban
% @Last Modified time: 2016-03-09 13:48:53

@@

\begin{document}
  \begin{tikzpicture}
    \node[inner sep=15pt, draw=black!40](fig06a) at (0,12.0)
      {\hspace*{20pt}\includegraphics[width=21cm]{figure06A}};
    \node[inner sep=15pt, draw=black!40](fig06b) at (0,0)
      {\hspace*{20pt}\includegraphics[width=21cm]{figure06B}};
    \node[circle, text=black!75, inner sep=0] at (-10.65,18.6) {\Huge \textbf{A}};
    \node[circle, text=black!75, inner sep=0] at (-10.65,3.5) {\Huge \textbf{B}};
  \end{tikzpicture}
\end{document}
